Cluster Difference Imaging Photometric Survey (CDIPS) II. TOI~837: A Young Validated Planet in IC~2602

### 2020-08-01 paper/ms.tex
minor

\begin{abstract}
  We report the discovery of TOI 837b and its validation as a
  transiting planet.  We characterize the system using data from the
  NASA TESS mission, the ESA Gaia mission, ground-based photometry
  from El Sauce and ASTEP400, and spectroscopy from CHIRON, FEROS, and
  Veloce.  We find that TOI 837 is a $T=9.9$ mag G0/F9 dwarf in the
  southern open cluster IC 2602.  The star and planet are therefore
  $35^{+11}_{-5}$ million years old.  Combining the transit photometry
  with a prior on the stellar parameters derived from the cluster
  color-magnitude diagram, we find that the planet has an orbital
  period of $8.3\,{\rm d}$ and is slightly smaller than Jupiter
  ($R_{\rm p} = 0.80^{+0.09}_{-0.03} \,R_{\rm Jup}$).  The transits
  are either grazing or nearly grazing.  From radial velocity
  monitoring, we limit $M_{\rm p}\sin i$ to less than 1.20 $M_{\rm
  Jup}$ (3-$\sigma$).  Grazing transits are a cause for concern, as
  they are often indicative of astrophysical false positive scenarios.
  Our follow-up data show that such scenarios are unlikely.
  Our combined multi-color photometry, high-resolution imaging, and
  radial velocities rule out hierarchical eclipsing binary scenarios.
  Background eclipsing binary scenarios, though limited by speckle
  imaging, remain a 0.2\% possibility.  TOI 837b is
  therefore a validated adolescent exoplanet.  The planetary nature of
  the system can be confirmed or refuted through observations of the
  stellar obliquity or the planetary mass.  Such observations may also
  improve our understanding of how the physical and orbital properties
  of exoplanets change in time.
\end{abstract}

>>>>

\begin{abstract}
  We report the discovery of TOI 837b and its validation as a
  transiting planet.  We characterize the system using data from the
  NASA TESS mission, the ESA Gaia mission, ground-based photometry
  from El Sauce and ASTEP400, and spectroscopy from CHIRON, FEROS, and
  Veloce.  We find that TOI 837 is a $T=9.9$ mag G0/F9 dwarf in the
  southern open cluster IC 2602.  The star and planet are therefore
  $35^{+11}_{-5}$ million years old.  Combining the transit photometry
  with a prior on the stellar parameters derived from the cluster
  color-magnitude diagram, we find that the planet has an orbital
  period of $8.3\,{\rm d}$ and is slightly smaller than Jupiter
  ($R_{\rm p} = 0.80^{+0.09}_{-0.03} \,R_{\rm Jup}$).  From radial
  velocity monitoring, we limit $M_{\rm p}\sin i$ to less than 1.20
  $M_{\rm Jup}$ (3-$\sigma$).  The transits either graze or nearly
  graze the stellar limb.  Grazing transits are a cause for concern,
  as they are often indicative of astrophysical false positive
  scenarios.  Our follow-up data show that such scenarios are
  unlikely.  Our combined multi-color photometry, high-resolution
  imaging, and radial velocities rule out hierarchical eclipsing
  binary scenarios.  Background eclipsing binary scenarios, though
  limited by speckle imaging, remain a 0.2\% possibility.  TOI 837b is
  therefore a validated adolescent exoplanet.  The planetary nature of
  the system can be confirmed or refuted through observations of the
  stellar obliquity and the planetary mass.  Such observations may also
  improve our understanding of how the physical and orbital properties
  of exoplanets change in time.
\end{abstract}
